### 2020-09-15 Manuscript/manuscript.tex
add Yavapai and Mazatzal to glossary

@@

>>>>

\noindent\textbf{Mazatzal orogen } An orogen resulting from latest Paleoproterozoic accretion of volcanic arc and back-arc terranes with southern Laurentia.

@@

\noindent\textbf{Yavapai orogen } An orogen resulting from Paleoproterozoic collision and accretion of oceanic arc terranes with southern Laurentia.
